---
title: "ETC5521 Assignment 1"
subtitle: ""
team: [Echidna]
author:
  - [Ruimin Lin]
  - [Rahul Bharadwaj]
date: "`r Sys.Date()`"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center')
library(tidyverse)
```

[This assignment is for ETC5521 Assignment 1 by Team `r rmarkdown::metadata$team` comprising of `r knitr::combine_words(rmarkdown::metadata$author)`.]{style="color:#006DAE;"}


## Introduction and motivation

* **What are the common characteristics of top ranked board games in each category and which is the best category of games in terms of average rating?**

The dataset contains multiple columns that consist of data such as max/min playtime, max/min players, min age of players that can play, game designer, game publisher, mechanics of the game and a lot more. The aim of this exploratory analysis is to find out what factor affect the average rating of games in each category and finally find the best category in terms of rating. This would give insights as to what games are most popular in each category and also about which category is most popular.

## Data description

```{r ReadData}
board_games <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-12/board_games.csv")
```

The board games data is obtained from the [Board Game Geek](https://boardgamegeek.com/) database. The dataset consists of `r ncol(board_games)` columns and `r nrow(board_games)` rows, in which there are `r ncol(board_games)` variables and `r nrow(board_games)` observations. The variables included in the data are as follows:

```{r}
glimpse(board_games)
```
The explanation of variables and variable types are provided to enable a better understanding of the variables in board games data set.

* game_id: ID of a particular game, the game_id should be a character vector(categorical) instead of a double vector mentioned in the table above.

* description: Game description, a character vector.

* image: URL image of the game, a character vector.

* max_players/min_player: maximum/minimum number of recommended players, double vectors.

* max_playtime/min_playtime: maximum/minimum recommended playtime, double vectors.

* min_age: recommended minimum player age, double vectors.

* name: name of the game, a character vector.

* playing_time: average playtime of a game, a double vector.

* thumbnail: URL thumbnail of the game, a character vector.

* year_published: year the game was published, a double vector.

* artist: artist for game art, a character vector.

* category: categories of the game, a character vector.

* compilation: name of compilation, a character vector.

* designer: game designer, a character vector.

* expansion: name of expansion pack (if any), a character vector.

* family: family of game - equivalent to a publisher, a character vector.

* mechanic: how game is played, a character vector.

* publisher: company/person who published the game, a character vector.

* average_rating: average rating from 1 to 10 on the website(Board Games Geek), a double vector.

* users_rated: number of users rated the game, a double vector.

This data set is cleaned by Thomas Mock, to ensure the reliability of the board game ratings, the data is limited to games with at least 50 ratings and for games between 1950 and 2016. The site's database has more than 90,000 games, with crowd-sourced ratings.

The original board games data set consists of 90400 observations, and 80 variables. Therefore, data cleaning and wrangling is necessary for data to enable better analysis procedure. Thomas have replaced long and complicate variable names like `details.description` in original data to `description` using `janitor::clean_names` and `set_names` function, which avoids messy code writing. In addition, Thomas have eliminated around 50 variables using function `select`, that leaves 27 variables at this stage.

The data set is then filtered to board games published from 1950 to 2016, with at least 50 users rated. NA values in variable `year_published` is also omitted. Thomas then excludes variables that may not be useful for the analysis, such as `attributes_total`, `game_type` etc., which ultimately, leaves us with a tidy data set (22 variables and 10532 variables) that is relatively concise and convenient for further exploration.
## Analysis and findings

[FILL] Should include at least one plot or numerical summary for each of your questions, that helps the reader arrive at an answer. You should also write paragraphs describing the methods, summaries and findings. 

## References
